Provenance analysis

### 2021-07-26 analysis/provenance2.Rmd
For the new provenance analysis

---
title: "Provenance"
author: "Pierre Donat-Bouillud"
output:
  html_document:
        gallery: false
        toc: true
        toc_depth: 3
        toc_float: true
        df_print: paged
date: "`r Sys.Date()`"
editor_options: 
  chunk_output_type: console
params:
  base_dir: Data/package/
  calls_path: summarized.fst
  corpus_path: corpus.txt
  static_path: evals-static.csv
  force_rebuild: FALSE
---

@@

@@

# Classification of provenance

## Expression types

```{r}
expressions <- E_prov %>% filter(type == "expression")

parsed_exprs <- expressions %>% filter(!is.na(parsed))

not_parsed_exprs <- expressions %>% anti_join(parsed_exprs)

nb_parsed_exprs_sites <- parsed_exprs %>% pull(src_ref) %>% n_distinct()

nb_not_parsed_exprs_sites <- not_parsed_exprs %>% pull(src_ref) %>% n_distinct()

overview_table(
    r("nb parse exprs sites", nb_parsed_exprs_sites),
    r("parse exprs site percent", ratio(nb_parsed_exprs_sites, nb_call_sites)),
    r("nb not parse exprs sites", nb_not_parsed_exprs_sites),
    r("not parse exprs site percent", ratio(nb_not_parsed_exprs_sites, nb_call_sites)),
)
```

## Language type

```{r}
languages <- E_prov %>% filter(type == "language")

match_call_exprs <- E_prov %>% filter(!is.na(match_call))

str2lang_exprs <- languages %>% filter(!is.na(parsed))

# Substitute, quote, bquote etc...
other_langs <- languages %>% anti_join(match_call_exprs) %>% anti_join(str2lang_exprs)

nb_match_call_exprs_sites <- match_call_exprs %>% pull(src_ref) %>% n_distinct()
nb_str2lang_sites <- str2lang_exprs %>% pull(src_ref) %>% n_distinct()
nb_other_langs_sites <- other_langs %>% pull(src_ref) %>% n_distinct()

overview_table(
    r("nb match call exprs sites", nb_match_call_exprs_sites),
    r("match call exprs site percent", ratio(nb_match_call_exprs_sites, nb_call_sites)),
    r("nb strlang sites", nb_str2lang_sites),
    r("strlang site percent", ratio(nb_str2lang_sites, nb_call_sites)),
    r("nb other langs sites", nb_other_langs_sites),
    r("other langs site percent", ratio(nb_other_langs_sites, nb_call_sites))
)
```

## Bytecode

We disable bytecode optimization so if we see a bytecode type, it means that `comp`has been explicitly called to compile to bytecode.

```{r}
bytecode_exprs <- E_prov %>% filter(type == "bytecode")

nb_bytecode_sites <- bytecode_exprs %>% pull(src_ref) %>% n_distinct()

overview_table(
    r("nb bytecode sites", nb_bytecode_sites),
    r("bytecode site percent", ratio(nb_bytecode_sites, nb_call_sites))
)
```

## Sites wwith less signficant provenance

```{r}
unknown_prov <- E_prov %>% anti_join(expressions) %>% anti_join(languages) %>% anti_join(bytecode_exprs)

nb_unknown_prov_sites <- unknown_prov %>% pull(src_ref) %>% n_distinct()

overview_table(
    r("nb unknown prov sites", nb_unknown_prov_sites),
    r("unknown prov site percent", ratio(nb_unknown_prov_sites, nb_call_sites))
)
```

# More details for `parse` and expressions

```{r}
parse_func_exprs <- parsed_exprs %>% filter(str_detect(parsed, fixed("parse")))
str2expression_exprs <- parsed_exprs %>% filter(str_detect(parsed, fixed("str2expression")))

nb_parse_func_sites <- parse_func_exprs %>% pull(src_ref) %>% n_distinct()
nb_str2expression_sites <- str2expression_exprs %>% pull(src_ref) %>% n_distinct()

# File qrgument (but ignore the srcfile one)
from_file_exprs <- parse_func_exprs %>% filter(str_detect(parsed, "\\bfile\\b"))
nb_from_file_sites <- from_file_exprs %>% pull(src_ref) %>% n_distinct()

overview_table(
    r("nb parse func sites", nb_parse_func_sites),
    r("parse func site percent", ratio(nb_parse_func_sites, nb_parsed_exprs_sites)),
    r("nb strexpression sites", nb_str2expression_sites),
    r("strexpression site percent", ratio(nb_str2expression_sites, nb_parsed_exprs_sites)),
    r("nb parse from file sites", nb_from_file_sites),
    r("parse from file site percent", ratio(nb_from_file_sites, nb_parse_func_sites))
)
```

# Another classification

```{r}
string_exprs <- E_prov %>% filter(!is.na(parsed))
nb_string_expr_sites <- n_distinct(string_exprs$src_ref)

constructed_exprs <- bind_rows(not_parsed_exprs, other_langs) %>% anti_join(match_call_exprs)
nb_constructed_expr_sites <- n_distinct(constructed_exprs$src_ref)

unknown_prov_exprs <- E_prov %>% anti_join(string_exprs) %>% anti_join(constructed_exprs) %>% anti_join(match_call_exprs)
nb_unknown_prov_exprs_sites <- n_distinct(unknown_prov_exprs$src_ref)

overview_table(
  r("nb constructed sites", nb_constructed_expr_sites),
  r("nb constructed site percent", ratio(nb_constructed_expr_sites, nb_call_sites)),
  r("nb string sites", nb_string_expr_sites),
  r("nb string site percent", ratio(nb_string_expr_sites, nb_call_sites)),
  r("nb unknown sites", nb_unknown_prov_exprs_sites),
  r("nb unknown site percent", ratio(nb_unknown_prov_exprs_sites, nb_call_sites)),
) 
# last category is match.call but we have it elsewhere
```

```{r}
duration <- difftime(Sys.time(), now)
```

Notebook execution was `r duration` `r units(duration)`.

>>>>

---
title: "Provenance analysis"
author: "Pierre Donat-Bouillud"
output:
  html_document:
        gallery: false
        toc: true
        toc_depth: 3
        toc_float: true
        df_print: paged
date: "`r Sys.Date()`"
editor_options: 
  chunk_output_type: console
params:
  base_dir: Data/package/
  calls_path: summarized.fst
  corpus_path: corpus.txt
  static_path: evals-static.csv
  force_rebuild: FALSE
---

@@

provenance_path <- paste0(params$base_dir, params$provenance_path)

@@
